Offshore Blue Crab Densities for <br/> The Gulf of Mexico

### 2020-01-10 2019_edits/R/offshore_analyses/crabs_per_hectare.Rmd
fixed toc
added likelihood ratio test

---
title: "Offshore Indices of Abundance for <br/> Blue Crabs"
author: "Adam A Kemberling"
date: "1/4/2020"
output: 
  html_document:
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

@@

## Model A. 2000-2018 w/ interaction

@@

### Fit Diagnostics - Deviance

@@

Percent Deviance for model A. = `r perc_dev`

#### CPUE Timeline

@@

### Observed vs. Predicted, all model factors

Model prediction (black) & observed mean values (blue), both standardized by overall mean

@@

## Model B. 2009-2018

@@

Percent Deviance for model B. = `r perc_dev`

#### CPUE Timeline

>>>>

---
title: "Offshore Blue Crab Densities for <br/> The Gulf of Mexico"
author: "Adam A Kemberling"
date: "1/4/2020"
output: 
  html_document:
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

@@

## Model A. 2000-2018 {.tabset}

@@

### Deviance

@@

**Percent Deviance for model A.** = `r perc_dev`

### Likelihood Ratio Test

Significance of the entire factor can be obtained by using a Chi-squared likelihood ratio test.

#Drop1 method
#drop1(mod1a, test = "F")     # F-test
#drop1(mod1a, test = "Chisq") # Chisq LRT - no scope

#Name what you want to drop
lrt_y  <- drop1(mod1a, scope = ~ year_f, test = "Chisq")
lrt_r  <- drop1(mod1a, scope = ~ region, test = "Chisq")
lrt_s  <- drop1(mod1a, scope = ~ season, test = "Chisq")
lrt_yr <- drop1(mod1a, scope = ~ year_f*region, test = "Chisq")

bind_rows(
  list(
    lrt_y  %>% as.data.frame() %>% 
      rownames_to_column(var = "Predictor"),
    lrt_r  %>% as.data.frame() %>% 
      rownames_to_column(var = "Predictor") %>% filter(Predictor == "region"),
    lrt_s  %>% as.data.frame() %>% 
      rownames_to_column(var = "Predictor") %>% filter(Predictor == "region"),
    lrt_yr  %>% as.data.frame() %>% 
      rownames_to_column(var = "Predictor") %>% filter(Predictor == "year_f:region")
)) %>% kable()

# #Anova method - LRT
# 
# # No interaction - testing
# mod1_test <- MASS:::glm.nb(sapidus_catch ~ year_f + region + season + 
#             offset(log(area_hectares)),
#             data = seamap_west)
# 
# anova(mod1a, mod1_test, test = "Chisq")
```

### CPUE Timeline

@@

### Observed vs. Predicted

Model prediction (black) & observed mean values (blue)

@@

## Model B. 2009-2018 {.tabset}

@@

**Percent Deviance for model B.** = `r perc_dev`

### Likelihood Ratio Test

#Drop1 method
#drop1(mod1a, test = "F")
#drop1(modb, test = "Chisq") # no scope

#Name what you want to drop
lrt_y  <- drop1(modb, scope = ~ year_f, test = "Chisq")
lrt_r  <- drop1(modb, scope = ~ region, test = "Chisq")
lrt_s  <- drop1(modb, scope = ~ season, test = "Chisq")
lrt_yr <- drop1(modb, scope = ~ year_f*region, test = "Chisq")

bind_rows(
  list(
    lrt_y  %>% as.data.frame() %>% 
      rownames_to_column(var = "Predictor"),
    lrt_r  %>% as.data.frame() %>% 
      rownames_to_column(var = "Predictor") %>% filter(Predictor == "region"),
    lrt_s  %>% as.data.frame() %>% 
      rownames_to_column(var = "Predictor") %>% filter(Predictor == "region"),
    lrt_yr  %>% as.data.frame() %>% 
      rownames_to_column(var = "Predictor") %>% filter(Predictor == "year_f:region")
)) %>% kable()

### CPUE Timeline
